Charm and bottom hadroproduction with heavy-quark mass renormalized in the $\overline{\rm MS}$ scheme

### 2019-06-26 papercharmrun.tex
updated figs

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{figs/parton-ptmax20/dyn-therr3/data_401-1.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-ptmax20/dyn-therr3-onlynom/data_401-1.pdf}}
    \includegraphics[width=0.49\textwidth]{figs/parton-ptmax20/dyn-therr3/data_401-2.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-ptmax20/dyn-therr3-onlynom/data_401-2.pdf}}\\
    \includegraphics[width=0.49\textwidth]{figs/parton-ptmax20/dyn-therr3/data_401-3.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-ptmax20/dyn-therr3-onlynom/data_401-3.pdf}}
    \includegraphics[width=0.49\textwidth]{figs/parton-ptmax20/dyn-therr3/data_401-4.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-ptmax20/dyn-therr3-onlynom/data_401-4.pdf}}
    \caption{The NLO differential cross sections for charm production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $c$ quark in the pole \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:c-pty-mu}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{figs/parton-b/dyn-therr3/data_401-1.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-b/dyn-therr3-onlynom/data_401-1.pdf}}
    \includegraphics[width=0.49\textwidth]{figs/parton-b/dyn-therr3/data_401-2.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-b/dyn-therr3-onlynom/data_401-2.pdf}}\\
    \includegraphics[width=0.49\textwidth]{figs/parton-b/dyn-therr3/data_401-3.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-b/dyn-therr3-onlynom/data_401-3.pdf}}
    \includegraphics[width=0.49\textwidth]{figs/parton-b/dyn-therr3/data_401-4.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-b/dyn-therr3-onlynom/data_401-4.pdf}}
    \caption{The NLO differential cross sections for bottom production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $b$ quark in the pole, \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:b-pty-mu}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{figs/parton-t/dyn-therr3/data_401-1.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-t/dyn-therr3-onlynom/data_401-1.pdf}}
    \includegraphics[width=0.49\textwidth]{figs/parton-t/dyn-therr3/data_401-2.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-t/dyn-therr3-onlynom/data_401-2.pdf}}\\
    \includegraphics[width=0.49\textwidth]{figs/parton-t/dyn-therr3/data_401-3.pdf}
    \put(-211,-44){\includegraphics[width=0.49\textwidth,trim=0 0 0 190,clip=true]{figs/parton-t/dyn-therr3-onlynom/data_401-3.pdf}}
    \caption{The NLO differential cross sections for top production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $t$ quark in the pole, \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:t-pty-mu}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=1.00\textwidth]{figs/parton-ptmax20/dyn-therr3-all.pdf}
    \caption{The NLO differential cross sections for charm production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $c$ quark in the pole \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:c-pty-mu}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.00\textwidth]{figs/parton-b/dyn-therr3-all.pdf}
    \caption{The NLO differential cross sections for bottom production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $b$ quark in the pole, \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:b-pty-mu}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.00\textwidth]{figs/parton-t/dyn-therr3-all.pdf}
    \caption{The NLO differential cross sections for top production with their scale uncertainties as a function of $p_T$ in intervals of $y$ of the $t$ quark in the pole, \msbar and MSR mass schemes at the LHC ($\sqrt{s} = 7$ TeV). The bottom panels display the theoretical predictions normalized to the values obtained in the pole mass scheme.}
    \label{fig:t-pty-mu}
\end{figure}
